Interactive Dashboard to Monitor the COVID-19 Outbreak and Vaccine Administration

### 2022-05-15 manuscript_covid19dashboard.Rmd
Completed paper

As of September 20th, 2021, 221 countries and territories are infected by the COVID-19 worldwide pandemic. Dashboards are the most often used visualization method for visualizing COVID-19 data and informing the public.  We explored 15 different dashboards.

@@

**Table 01: Labeled of the Dashboards**

@@

**Table 04: Comparison of visualization tools & features of dashboard**

@@

```{r, comment=NA, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Distribution of COVID19 Cases by Districts: (A) Plotted on a Single Panel, (B) Plotted on Separate Panels.", fig.height=12, fig.width=10}
library(covid19srilanka)
library(tidyverse)
data("district.wise.cases")
f2 <- ggplot(district.wise.cases, aes(
  x=Date, y=Count)) + geom_line() + 
  facet_wrap(vars(District), scale="free", ncol=5) + ggtitle("B")
f1/f2
```

@@

```{r, echo=FALSE,fig.cap="(A) Global View of Distribution of COVID19 Cases by DIstricts, (B) Local View of Distribution of COVID19 Cases by Districts", fig.width=10, fig.height=10}

@@

```{r, comment=NA, message=FALSE, warning=FALSE, fig.cap="Spatial DIstribution of COVID1-19 Cases by Districts", fig.height=8}

@@

```{r, echo=FALSE, fig.cap="Screeshot of Panel 1: Overview", out.width="80%", fig.align='center'}
knitr::include_graphics("Images/image1.png")
```

```{r, echo=FALSE, fig.cap="Screeshot of Panel 2: Cases by Wave", out.width="80%", fig.align='center'}
knitr::include_graphics("Images/image2.png")
```

```{r, echo=FALSE, fig.cap="Screeshot of Panel 3: Distribution of COVID-19 Patients", out.width="80%", fig.align='center'}
knitr::include_graphics("Images/image3.png")
```

```{r, echo=FALSE, fig.cap="Screeshot of Panel 4: Vaccination Details", out.width="80%", fig.align='center'}
knitr::include_graphics("Images/image4.png")
```

```{r, echo=FALSE, fig.cap="Screeshot of Panel 5: Comparison with Top 10 Countries", out.width="80%", fig.align='center'}
knitr::include_graphics("Images/image5.png")
```

```{r, echo=FALSE, fig.cap="Screeshot of Panel 6: Global Comparison", out.width="80%", fig.align='center'}
knitr::include_graphics("Images/image6.png")
```

```{r, echo=FALSE, fig.cap="Screeshot of Panel 7: World Map", out.width="80%", fig.align='center'}
knitr::include_graphics("Images/image7.png")
```

```{r, echo=FALSE, fig.cap="Screeshot of Panel 8: About", out.width="80%", fig.align='center'}
knitr::include_graphics("Images/image8.png")
```

@@

When building our dashboard we use a colour-blind friendly theme. Our dashboard is fully reproducible. The source code to reprouduce the results are available in a public GitHub repository and can be accessonline via https://github.com/thiyangt/covid19srilanka

>>>>

Dashboards are the most common visualization method for displaying COVID-19 data and informing the public. We examined 15 different dashboards to see how various visualization techniques were used. This paper describes the creation and implementation of a dashboard for COVID-19 epidemic and vaccination administration data in Sri Lanka.

@@

**Table 01: Labels of the dashboards**

@@

**Table 04: Comparison of visualization tools and features of dashboard**

@@

```{r, comment=NA, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Distribution of COVID-19 cases by districts: (A) Plotted on a single panel, (B) Plotted on separate panels.", fig.height=12, fig.width=10}
library(covid19srilanka)
library(tidyverse)
data("district.wise.cases")
f2 <- ggplot(district.wise.cases, aes(
  x=Date, y=Count)) + geom_line() + 
  facet_wrap(vars(District), scale="free", ncol=5) + ggtitle("B")
f1/f2
```

@@

```{r, echo=FALSE,fig.cap="(A) Global view of distribution of COVID-19 cases by districts, (B) Local view of distribution of COVID-19 cases by districts", fig.width=10, fig.height=10}

@@

```{r, comment=NA, message=FALSE, warning=FALSE, fig.cap="Spatial distribution of COVID1-19 cases by districts", fig.height=8}

@@

```{r, echo=FALSE, fig.cap="Screeshot of panel 1: Overview", out.width="80%", fig.align='center'}
knitr::include_graphics("Images/image1.png")
```

```{r, echo=FALSE, fig.cap="Screeshot of panel 2: Cases by Wave", out.width="80%", fig.align='center'}
knitr::include_graphics("Images/image2.png")
```

```{r, echo=FALSE, fig.cap="Screeshot of panel 3: Distribution of COVID-19 Patients", out.width="80%", fig.align='center'}
knitr::include_graphics("Images/image3.png")
```

```{r, echo=FALSE, fig.cap="Screeshot of panel 4: Vaccination Details", out.width="80%", fig.align='center'}
knitr::include_graphics("Images/image4.png")
```

```{r, echo=FALSE, fig.cap="Screeshot of panel 5: Comparison with Top 10 Countries", out.width="80%", fig.align='center'}
knitr::include_graphics("Images/image5.png")
```

```{r, echo=FALSE, fig.cap="Screeshot of Panel 6: Global comparison", out.width="80%", fig.align='center'}
knitr::include_graphics("Images/image6.png")
```

```{r, echo=FALSE, fig.cap="Screeshot of panel 7: World Map", out.width="80%", fig.align='center'}
knitr::include_graphics("Images/image7.png")
```

```{r, echo=FALSE, fig.cap="Screeshot of panel 8: About", out.width="80%", fig.align='center'}
knitr::include_graphics("Images/image8.png")
```

@@

We used a color-blind-friendly theme when creating our dashboard. The dashboard includes both static and interactive charts that can be used for explanation, exploration, and display. The data speaks to us, but it is not always easy to understand in what language they are doing it. Hence, we examine the same data under different angles using different types of plots. We do not have district-wise vaccination details. We do not have vaccination information per district. We'll save this for later. Our dashboard is completely replicable. The source code for reproducing the results is accessible in a public GitHub repository at https://github.com/thiyangt/covid19srilanka.

### 2022-05-15 manuscript_covid19dashboard.tex
Completed paper

\textbf{Table 01: Labeled of the Dashboards}

@@

\textbf{Table 04: Comparison of visualization tools \& features of
dashboard}

@@

\begin{figure}
\centering
\includegraphics{manuscript_covid19dashboard_files/figure-latex/unnamed-chunk-2-1.pdf}
\caption{Distribution of COVID19 Cases by Districts: (A) Plotted on a
Single Panel, (B) Plotted on Separate Panels.}
\end{figure}

\begin{figure}
\centering
\includegraphics{manuscript_covid19dashboard_files/figure-latex/unnamed-chunk-3-1.pdf}
\caption{(A) Global View of Distribution of COVID19 Cases by DIstricts,
(B) Local View of Distribution of COVID19 Cases by Districts}
\end{figure}

\begin{figure}
\centering
\includegraphics{manuscript_covid19dashboard_files/figure-latex/unnamed-chunk-4-1.pdf}
\caption{Spatial DIstribution of COVID1-19 Cases by Districts}
\end{figure}

@@

\caption{Screeshot of Panel 1: Overview}\label{fig:unnamed-chunk-5}
\end{figure}

@@

\caption{Screeshot of Panel 2: Cases by Wave}\label{fig:unnamed-chunk-6}
\end{figure}

@@

\caption{Screeshot of Panel 3: Distribution of COVID-19 Patients}\label{fig:unnamed-chunk-7}
\end{figure}

@@

\caption{Screeshot of Panel 4: Vaccination Details}\label{fig:unnamed-chunk-8}
\end{figure}

@@

\caption{Screeshot of Panel 5: Comparison with Top 10 Countries}\label{fig:unnamed-chunk-9}
\end{figure}

@@

\caption{Screeshot of Panel 6: Global Comparison}\label{fig:unnamed-chunk-10}
\end{figure}

@@

\caption{Screeshot of Panel 7: World Map}\label{fig:unnamed-chunk-11}
\end{figure}

@@

\caption{Screeshot of Panel 8: About}\label{fig:unnamed-chunk-12}
\end{figure}

@@

When building our dashboard we use a colour-blind friendly theme. Our
dashboard is fully reproducible. The source code to reprouduce the
results are available in a public GitHub repository and can be
accessonline via \url{https://github.com/thiyangt/covid19srilanka}

>>>>

\textbf{Table 01: Labels of the dashboards}

@@

\textbf{Table 04: Comparison of visualization tools and features of
dashboard}

@@

\begin{figure}
\centering
\includegraphics{manuscript_covid19dashboard_files/figure-latex/unnamed-chunk-2-1.pdf}
\caption{Distribution of COVID-19 cases by districts: (A) Plotted on a
single panel, (B) Plotted on separate panels.}
\end{figure}

\begin{figure}
\centering
\includegraphics{manuscript_covid19dashboard_files/figure-latex/unnamed-chunk-3-1.pdf}
\caption{(A) Global view of distribution of COVID-19 cases by districts,
(B) Local view of distribution of COVID-19 cases by districts}
\end{figure}

\begin{figure}
\centering
\includegraphics{manuscript_covid19dashboard_files/figure-latex/unnamed-chunk-4-1.pdf}
\caption{Spatial distribution of COVID1-19 cases by districts}
\end{figure}

@@

\caption{Screeshot of panel 1: Overview}\label{fig:unnamed-chunk-5}
\end{figure}

@@

\caption{Screeshot of panel 2: Cases by Wave}\label{fig:unnamed-chunk-6}
\end{figure}

@@

\caption{Screeshot of panel 3: Distribution of COVID-19 Patients}\label{fig:unnamed-chunk-7}
\end{figure}

@@

\caption{Screeshot of panel 4: Vaccination Details}\label{fig:unnamed-chunk-8}
\end{figure}

@@

\caption{Screeshot of panel 5: Comparison with Top 10 Countries}\label{fig:unnamed-chunk-9}
\end{figure}

@@

\caption{Screeshot of Panel 6: Global comparison}\label{fig:unnamed-chunk-10}
\end{figure}

@@

\caption{Screeshot of panel 7: World Map}\label{fig:unnamed-chunk-11}
\end{figure}

@@

\caption{Screeshot of panel 8: About}\label{fig:unnamed-chunk-12}
\end{figure}

@@

We used a color-blind-friendly theme when creating our dashboard. The
dashboard includes both static and interactive charts that can be used
for explanation, exploration, and display. The data speaks to us, but it
is not always easy to understand in what language they are doing it.
Hence, we examine the same data under different angles using different
types of plots. We do not have district-wise vaccination details. We do
not have vaccination information per district. We'll save this for
later. Our dashboard is completely replicable. The source code for
reproducing the results is accessible in a public GitHub repository at
\url{https://github.com/thiyangt/covid19srilanka}.
